INSTALLATION OF ANACONDA.

Download(https://www.anaconda.com/products/distribution#windows ). follow the instructions
Always create ENVIRONMENTS. Use pip to install libraries in that environment.
Anaconda is not an IDE. its a distribution. Conda has its own ide - Spyder, its fairly good.
if you get stucked any where you can follow (https://www.geeksforgeeks.org/how-to-install-anaconda-on-windows/), or cant follow - watch (https://www.youtube.com/watch?v=y7KtVULjH_U)

BASIS OF CONDA ENVIRONMENT.
Conda is an open source package management system and environment management system that runs on Windows, macOS, Linux and z/OS. Conda quickly installs, runs and updates packages and their dependencies. Conda easily creates, saves, loads and switches between environments on your local computer. It was created for Python programs, but it can package and distribute software for any language.Conda is also included in Anaconda Enterprise, which provides on-site enterprise package and environment management for Python, R, Node.js, Java and other application stacks. Conda is also available on conda-forge, a community channel. You may also get conda on PyPI, but that approach may not be as up to date.If you need a package that requires a different version of Python, you do not need to switch to a different environment manager, because conda is also an environment manager. With just a few commands, you can set up a totally separate environment to run that different version of Python, while continuing to run your usual version of Python in your normal environment.
 * FOR MORE YOU CAN EXPLORE(https://docs.conda.io/projects/conda/en/latest/) 
